---
title: "5 - FERC robustness"
author: "Albert Planting-Gyllenbaga (41669)"
date: "26/04/2021"
output: html_document
---

```{r}
library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(directlabels)
library(purrr)
library(fBasics)
library(Hmisc)
library(plm)
library(stargazer)
library(lmtest)
library(sandwich)
library(car)
library(scales)
library(DescTools)
library(ggrepel)
```


Load and adjust data
```{r}
# Clear data
rm(list=ls())

# Load data
df = read.delim2("dataset_interacted.csv", sep = ",")
sync = read.delim2("nsynch.csv", sep = ",")

# Adjust classes
x = colnames(df)
x = x[!(x %in% c("COMNAM"))]

for (i in x) {
  df[[i]] = as.numeric(as.character(df[[i]]))
}

x = c("year", "PERMCO", "GVKEY", "sic4", "sic3", "sic2", "sic1", "naics4")

for (i in x) {
  df[[i]] = factor(df[[i]])
}

# Adjust sync
sync$nsynch = as.numeric(as.character(sync$nsynch))
sync$year = factor(sync$year)
sync$PERMCO = factor(sync$PERMCO)
sync$id = paste(sync$year, sync$PERMCO)
sync = sync[!duplicated(sync$id),]

# Rename NEST and size
colnames(df) = gsub("NEST", "nest", colnames(df))
colnames(df) = gsub("S", "Sz", colnames(df))

# Merge in sync
df = left_join(df, sync[c("year", "PERMCO", "nsynch")], by = c("year", "PERMCO"))
```


Basic stats of robustnesses
```{r}
# Create summary stats
x = df %>% select(lc4, lc_naics, EBIT_l, EBIT_t, EBIT3, EBITDA4, R4,
                  nsynch)
stats = basicStats(x)
stats = round(stats, 2)
stats <- stats[c("Minimum", "1. Quartile","Median", "3. Quartile",
                 "Maximum", "Mean", "Stdev"),]
stats = t(stats)

# Rename to latex
colnames(stats) = c("Min", "25\\textsuperscript{th}", "Median", "75\\textsuperscript{th}",
                    "Max", "Mean", "SD")
rownames(stats) = c("4-digit SIC $LC_{t}$", "NAICS $LC_{t}$",
                    "$EBIT_{t-1}$", "$EBIT_{t}$", "$EBIT3_{t}$",
                    "$E4_{t}$", "$R4_{t}$", "$NSYNCH_{t}$")

# Summary stats table
stargazer(stats, type = "latex")
```



Create FERC function
```{r}
# Drop other variables that should not be included in the basic formula
exc = c("r0", "PERMCO", "GVKEY", "sic4", "sic3", "sic2", "sic1", "tlist3", "tlist4",
      "year", "fyr", "hhi", "naics", "tlist3l")
exc = colnames(df)[!(colnames(df) %in% exc)]
all = exc
exc = exc[!grepl("xrd", exc)]
#exc = exc[!grepl("int", exc)]
exc = exc[!grepl("div", exc)]
exc = exc[!grepl("indto", exc)]
exc = exc[!grepl("naics", exc)]
exc = exc[!grepl("R4", exc)]
exc = exc[!grepl("EBITDA4", exc)]
exc = exc[!grepl("EBIT_", exc)]
exc = exc[!grepl("EBIT3", exc)]
exc = exc[!grepl("lc4", exc)]
exc = exc[!grepl("nsynch", exc)]
exc = exc[!grepl("lc3l", exc)]

# Add interacted dummies
exc2 = c(exc, "sic1", "sic1:EBITDA_l", "sic1:EBITDA_t", "sic1:EBITDA3", "sic1:R3",
         "year", "year:EBITDA_l", "year:EBITDA_t", "year:EBITDA3", "year:R3")

# Create formula for full model with all controls
f <- as.formula(paste("r0 ~", paste(exc, collapse = " + ")))
f

# Drop mediators
exc = exc[!grepl("nest", exc)]
exc = exc[!grepl("to", exc)]

# Add interacted dummies
exc1 = c(exc, "sic1", "sic1:EBITDA_l", "sic1:EBITDA_t", "sic1:EBITDA3", "sic1:R3",
         "year", "year:EBITDA_l", "year:EBITDA_t", "year:EBITDA3", "year:R3")

# Create formula with no controls
exc0 = c("EBITDA_l", "EBITDA_t", "EBITDA3", "R3", "lc3", "lc3_EBITDA_l",
         "lc3_EBITDA_t", "lc3_EBITDA3", "lc3_R3")


# Create labels
ctrl = c('Controls', "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")
media = c('Mediators', "No", "No", "Yes", "No", "No", "No", "No")
inds = c('Industry dummies', "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")
fe = c('Year fixed effects', "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")
se = c('Adjusted SE', "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")
```


Robustness: include mediator variables
```{r}
# Create containers
mods_med = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run basic model
f <- as.formula(paste("r0 ~", paste(exc1, collapse = " + ")))
n = 1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_med[[n]] = mod


# Create formula with analyst estimates
x = c(exc1, all[grepl("nest", all)])
x = x[!grepl("EBIT_", x)]
x = x[!grepl("EBIT3", x)]
x = x[!grepl("EBITDA4", x)]
x = x[!grepl("R4", x)]
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Reposition mediator vars to the end of the dataset
x = df[grepl("to", colnames(df))]
df = df[!grepl("to", colnames(df))]
df = cbind(df, x)

x = df[grepl("nest", colnames(df))]
df = df[!grepl("nest", colnames(df))]
df = cbind(df, x)


# Run analyst estimates model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_med[[n]] = mod



# Create formula with turnover
x = c(exc1, all[grepl("to", all)])
x = x[!grepl("indto", x)]
x = x[!grepl("EBIT_", x)]
x = x[!grepl("EBIT3", x)]
x = x[!grepl("EBITDA4", x)]
x = x[!grepl("R4", x)]
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Run turnover model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_med[[n]] = mod



# Create formula with both
x = c(exc1, all[grepl("nest", all)])
x = c(x, all[grepl("to", all)])
x = x[!grepl("indto", x)]
x = x[!grepl("EBIT_", x)]
x = x[!grepl("EBIT3", x)]
x = x[!grepl("EBITDA4", x)]
x = x[!grepl("R4", x)]
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Run model with both mediators
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_med[[n]] = mod


# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_med,
          type="latex",
          omit = c("Cons", "_W__", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E3_{t}$", "$R3_{t}$",
                                "$LC_{t}$", "$LC_{t}*E_{t-1}$", "$LC_{t}*E_{t}$",
                                "$LC_{t}*E3_{t}$", "$LC_{t}*R3_{t}$",
                                "$NEST_{t}$", "$NEST_{t}*E_{t-1}$", "$NEST_{t}*E_{t}$",
                                "$NEST_{t}*E3_{t}$", "$NEST_{t}*R3_{t}$",
                                "$TO_{t}$", "$TO_{t}*E_{t-1}$", "$TO_{t}*E_{t}$",
                                "$TO_{t}*E3_{t}$", "$TO_{t}*R3_{t}$"),
          add.lines=list(#c('Size controls', rep("Yes",rep)),
                         #c('HHI controls', rep("Yes", rep)),
                         #c('M/B ratio controls', rep("Yes", rep)),
                         c('Controls', rep("Yes", rep)),
                         c('Industry dummies', rep("Yes", rep)),
                         c('Year fixed effects', rep("Yes", rep)),
                         c('Adjusted SE', rep("Yes", rep)),
                         c("Observations", n),
                         c("Adjusted R2", r2)))
```


Robustness: change to lagged industry classifications
```{r}
# Create formula with 4-digit listings
x = gsub("lc3", "lc3l", exc1)
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create formula with mediators
x = gsub("lc3", "lc3l", exc2)
f2 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create base formula with 4-digit listings
x = gsub("lc3", "lc3l", exc0)
f0 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create containers
mods_lc3l = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run 4-digit base model
n = 1
mod = lm(f0, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_lc3l[[n]] = mod

# Run 4-digit model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_lc3l[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_lc3l[[n]] = mod


# Run 2011
z = subset(df, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_lc3l[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_lc3l[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_lc3l[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_lc3l,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E3_{t}$", "$R3_{t}$",
                                 "$LC_{t-1}$",
                                 "$LC_{t-1}*E_{t-1}$",
                                 "$LC_{t-1}*E_{t}$",
                                 "$LC_{t-1}*E3_{t}$",
                                 "$LC_{t-1}*R3_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))
```



Robustness: change to 4- digit industry classifications
```{r}
# Create formula with 4-digit listings
x = gsub("lc3", "lc4", exc1)
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create formula with mediators
x = gsub("lc3", "lc4", exc2)
f2 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create base formula with 4-digit listings
x = gsub("lc3", "lc4", exc0)
f0 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create containers
mods_sic4 = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run 4-digit base model
n = 1
mod = lm(f0, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic4"))
mods_sic4[[n]] = mod

# Run 4-digit model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic4"))
mods_sic4[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic4"))
mods_sic4[[n]] = mod

# Run 2011
z = subset(df, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic4"))
mods_sic4[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic4"))
mods_sic4[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic4"))
mods_sic4[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_sic4,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E3_{t}$", "$R3_{t}$",
                                 "4-digit SIC $LC_{t}$",
                                 "4-digit SIC $LC_{t}*E_{t-1}$",
                                 "4-digit SIC $LC_{t}*E_{t}$",
                                 "4-digit SIC $LC_{t}*E3_{t}$",
                                 "4-digit SIC $LC_{t}*R3_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))
```



Robustness: change to NAICS industry classifications
```{r}
# Create formula
x = gsub("lc3_", "lcnaics_", exc1)
x = gsub("lc3", "lc_naics", x)
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create formula with mediators
x = gsub("lc3_", "lcnaics_", exc2)
x = gsub("lc3", "lc_naics", x)
f2 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create base formula
x = gsub("lc3_", "lcnaics_", exc0)
x = gsub("lc3", "lc_naics", x)
f0 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create containers
mods_naics = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run base model
n = 1
mod = lm(f0, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "naics4"))
mods_naics[[n]] = mod

# Run model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "naics4"))
mods_naics[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "naics4"))
mods_naics[[n]] = mod

# Run 2011
z = subset(df, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "naics4"))
mods_naics[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "naics4"))
mods_naics[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "naics4"))
mods_naics[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_naics,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E3_{t}$", "$R3_{t}$",
                                 "NAICS $LC_{t}$",
                                 "NAICS $LC_{t}*E_{t-1}$",
                                 "NAICS $LC_{t}*E_{t}$",
                                 "NAICS $LC_{t}*E3_{t}$",
                                 "NAICS $LC_{t}*R3_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))
```




Robustness: new IPOs
```{r}
# Drop 
y = subset(df, age > 1)

# Create formulas
f <- as.formula(paste("r0 ~", paste(exc1, collapse = " + ")))
f2 <- as.formula(paste("r0 ~", paste(exc2, collapse = " + ")))
f0 <- as.formula(paste("r0 ~", paste(exc0, collapse = " + ")))

# Create containers
mods_old = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run base model
n = 1
mod = lm(f0, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_old[[n]] = mod

# Run model
n = n+1
mod = lm(f, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_old[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_old[[n]] = mod

# Run 2011
z = subset(y, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_old[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_old[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_old[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_old,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E3_{t}$", "$R3_{t}$",
                                 "$LC_{t}$",
                                 "$LC_{t}*E_{t-1}$",
                                 "$LC_{t}*E_{t}$",
                                 "$LC_{t}*E3_{t}$",
                                 "$LC_{t}*R3_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))

```







Robustness: exclude utilities
```{r}
# Drop utilities
y = subset(df, sic1 != "4")

# Create formulas
f <- as.formula(paste("r0 ~", paste(exc1, collapse = " + ")))
f2 <- as.formula(paste("r0 ~", paste(exc2, collapse = " + ")))
f0 <- as.formula(paste("r0 ~", paste(exc0, collapse = " + ")))

# Create containers
mods_ut = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run base model
n = 1
mod = lm(f0, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ut[[n]] = mod

# Run model
n = n+1
mod = lm(f, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ut[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ut[[n]] = mod


# Run 2011
z = subset(y, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ut[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ut[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ut[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_ut,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E3_{t}$", "$R3_{t}$",
                                 "$LC_{t}$",
                                 "$LC_{t}*E_{t-1}$",
                                 "$LC_{t}*E_{t}$",
                                 "$LC_{t}*E3_{t}$",
                                 "$LC_{t}*R3_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))

```


Robustness: fiscal year ends 31 dec
```{r}
# Drop other year ends
y = subset(df, fyr == 12)

# Create formulas
f <- as.formula(paste("r0 ~", paste(exc1, collapse = " + ")))
f2 <- as.formula(paste("r0 ~", paste(exc2, collapse = " + ")))
f0 <- as.formula(paste("r0 ~", paste(exc0, collapse = " + ")))

# Create containers
mods_fy = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run base model
n = 1
mod = lm(f0, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_fy[[n]] = mod

# Run model
n = n+1
mod = lm(f, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_fy[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_fy[[n]] = mod

# Run 2011
z = subset(y, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_fy[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_fy[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_fy[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_fy,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E3_{t}$", "$R3_{t}$",
                                 "$LC_{t}$",
                                 "$LC_{t}*E_{t-1}$",
                                 "$LC_{t}*E_{t}$",
                                 "$LC_{t}*E3_{t}$",
                                 "$LC_{t}*R3_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))

```




Robustness: change to EBIT
```{r}
# Create formula 
x = gsub("EBITDA", "EBIT", exc1)
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create formula with mediators
x = gsub("EBITDA", "EBIT", exc2)
f2 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create base formula
x = gsub("EBITDA", "EBIT", exc0)
f0 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create containers
mods_ebit = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run base model
n = 1
mod = lm(f0, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ebit[[n]] = mod

# Run model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ebit[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ebit[[n]] = mod

# Run 2011
z = subset(df, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ebit[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ebit[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_ebit[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_ebit,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$EBIT_{t-1}$", "$EBIT_{t}$", "$EBIT3_{t}$", "$R3_{t}$",
                                 "$LC_{t}$",
                                 "$LC_{t}*EBIT_{t-1}$",
                                 "$LC_{t}*EBIT_{t}$",
                                 "$LC_{t}*EBIT3_{t}$",
                                 "$LC_{t}*R3_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))
```



Robustness: change to 4 future returns/earnings
```{r}
# Create formula 
x = gsub("EBITDA3", "EBITDA4", exc1)
x = gsub("R3", "R4", x)
f <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create formula with mediators
x = gsub("EBITDA3", "EBITDA4", exc2)
x = gsub("R3", "R4", x)
f2 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create base formula
x = gsub("EBITDA3", "EBITDA4", exc0)
x = gsub("R3", "R4", x)
f0 <- as.formula(paste("r0 ~", paste(x, collapse = " + ")))

# Create containers
mods_4l = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run base model
n = 1
mod = lm(f0, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_4l[[n]] = mod

# Run model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_4l[[n]] = mod

# Run mediator model
n = n+1
mod = lm(f2, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_4l[[n]] = mod

# Run 2011
z = subset(df, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_4l[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_4l[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_4l[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_4l,
          type="latex",
          omit = c("Cons", "_W_", "sic", "Sz", "prc_xrd", "age", "MB", "L", "hhi",
                   "19", "20", "int", "nest", "to"),
          model.names = F,
          dep.var.labels.include = F,
          dep.var.caption = "",
          omit.stat=c("f", "ser", "rsq"),
          covariate.labels = c("$E_{t-1}$", "$E_{t}$", "$E4_{t}$", "$R4_{t}$",
                                 "$LC_{t}$",
                                 "$LC_{t}*E_{t-1}$",
                                 "$LC_{t}*E_{t}$",
                                 "$LC_{t}*E4_{t}$",
                                 "$LC_{t}*R4_{t}$"),
          add.lines=list(#c('Size controls', "No", "Yes"),
                         #c('HHI controls', "No", "Yes"),
                         #c('M/B ratio controls', "No", "Yes"),
                         ctrl,
                         media,
                         inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))
```






Robustness: Non-synchronicity
```{r}
# Create formulas
f = as.formula("nsynch ~ lc3 + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")
f0 = as.formula("nsynch ~ lc3")

# Create containers
mods_sync = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run base model
n = 1
mod = lm(f0, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_sync[[n]] = mod

# Run model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_sync[[n]] = mod


# Create formula with mediators
f = as.formula("nsynch ~ lc3 + nest + to + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")

# Run model
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_sync[[n]] = mod


# Run 2011
z = subset(df, as.numeric(as.character(year)) >2010)
n = n+1
mod = lm(f, data = z)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_sync[[n]] = mod

# Run high MB
z = z %>% mutate(rank_MB = percent_rank(MB))
a = subset(z, rank_MB >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_sync[[n]] = mod

# Run high int
z = z %>% mutate(rank_int = percent_rank(prc_int))
a = subset(z, rank_int >0.75)
n = n+1
mod = lm(f, data = a)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0", cluster = "sic3"))
mods_sync[[n]] = mod

# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_sync,
          type="latex",
          omit = c("sic", "19", "20"),
          model.names = F,
          #dep.var.labels.include = F,
          dep.var.caption = "Dependent variable: $NSYNCH_{t}$",
          omit.stat=c("f", "ser", "rsq", "n", "adj.rsq"),
          covariate.labels = c("$LC_{t}$", "$NEST_{t}$", "$TO_{t}$",
                                "$S_{t}$", "$HHI_{t}$", "$M/B_{t}$",
                                "$IndMB_{t}$", "$Int_{t}$",
                                "$Age_{t}$", "$IndAge_{t}$",
                                "$L_{t}$", "Constant"),
          add.lines=list(inds,
                         fe,
                         se,
                         c("Observations", n),
                         c("Adjusted R2", r2)))

```



Robustness: Non-synchronicity - robustnesses
```{r}
# Create containers
mods_sync2 = list()
obs = as.data.frame(matrix(nrow = 2, ncol = 3))

# Run model with lagged listings
f = as.formula("nsynch ~ lc3l + nest + to + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")
n = 1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0"))
mods_sync2[[n]] = mod

# Run model with 4-digit listings
f = as.formula("nsynch ~ lc4 + nest + to + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0"))
mods_sync2[[n]] = mod

# Run model with naics listings
f = as.formula("nsynch ~ lc_naics + nest + to + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")
n = n+1
mod = lm(f, data = df)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0"))
mods_sync2[[n]] = mod

# Run model excluding new ipos
y = subset(df, age > 1)
f = as.formula("nsynch ~ lc3 + nest + to + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")
n = n+1
mod = lm(f, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0"))
mods_sync2[[n]] = mod

# Run model excluding utilities
y = subset(df, sic1 != "4")
f = as.formula("nsynch ~ lc3 + nest + to + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")
n = n+1
mod = lm(f, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0"))
mods_sync2[[n]] = mod


# Run model excluding non 31 dec fiscal years
y = subset(df, fyr == 12)
f = as.formula("nsynch ~ lc3 + nest + to + Sz + hhi2 + MB + indMB + prc_int + age +
           indage + L + sic1 + year")
n = n+1
mod = lm(f, data = y)
obs[1, n] = nobs(mod)
obs[2, n] = summary(mod)$r.squared
mod = coeftest(mod, vcov = vcovHC(mod, type = "HC0"))
mods_sync2[[n]] = mod


# Create table
n = as.numeric(unlist(obs[1,]))
r2 = as.numeric(unlist(obs[2,]))
r2 = format(round(r2, digits=2), nsmall = 2) 

rep = 10
stargazer(mods_sync2,
          type="latex",
          omit = c("sic", "19", "20"),
          model.names = F,
          #dep.var.labels.include = F,
          dep.var.caption = "Dependent variable: $NSYNCH_{t}$",
          omit.stat=c("f", "ser", "rsq", "n", "adj.rsq"),
          covariate.labels = c("$LC_{t-1}$", "4-digit SIC $LC_{t}$", "NAICS $LC_{t}$",
                               "$LC_{t}$", "$NEST_{t}$", "$TO_{t}$",
                                "$S_{t}$", "$HHI_{t}$", "$M/B_{t}$",
                                "$IndMB_{t}$", "$Int_{t}$",
                                "$Age_{t}$", "$IndAge_{t}$",
                                "$L_{t}$", "Constant"),
          add.lines=list(c('Industry dummies', "No", "Yes", "Yes", "Yes", "Yes"),
                         c('Year fixed effects', "No", "Yes", "Yes", "Yes", "Yes"),
                         c('Adjusted SE', rep("Yes", 10)),
                         c("Observations", n),
                         c("Adjusted R2", r2)))

```
